ext_risk_copula

### 2019-02-16 ext_risk_copula.Rmd
all cleaned code as of now with plotting avg acf for pop

pdf("./Results/hassell/hassell_extrisk_d0.pdf",height = 6,width=6)
plot(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = c(1.4,7.6),xlab="r",ylab="ext_risk",cex.lab=1.5,pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025left,x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_hassell,lty="dotted")

@@

pdf(paste(resloc,"msmith_extrisk_d0.pdf",sep=""),height=6,width=6)
plot(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = c(1.2,2.8),xlab="r",ylab="ext_risk",cex.lab=1.5,pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025left,x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_msmith,lty="dotted")

@@

```{r fig_pennycuick, echo=F,  results="hide", cache=T, cache.extra=list(seed,a_pennycuick,b_pennycuick,rc_pennycuick,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
model<-"pennycuick"

@@

# plot for local dispersal in D matrix 
pdf(paste(resloc,"pennycuick_ext_risk_local_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.2))
for(i in c(1:length(rlist))){
    r<-rlist[i]
    params<-c(r,a,b)
    K_e<-(b/a)*(a+log(r-1))
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,ploton = F)
    pennycuick_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    pennycuick_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

saveRDS(pennycuick_extrisk_d0,paste(resloc,"pennycuick_extrisk_d0.RDS",sep=""))

# plot for global dispersal in D matrix 
pdf(paste(resloc,"pennycuick_ext_risk_global_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.2))
for(r in rlist){
    params<-c(r,a,b)
    K_e<-(b/a)*(a+log(r-1))
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

@@

pdf("./Results/pennycuick/pennycuick_extrisk_d0.pdf",height = 6,width=6)
plot(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = c(2,7),xlab="r",ylab="ext_risk",cex.lab=1.5,pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025left,x1=pennycuick_extrisk_d0$r,y1=pennycuick_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)

@@

```{r fig_abrewer_scl_0.8, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)

@@

numsims<-10000
numsteps<-25
numlocs<-5
s<-0.2
K<-50
p0<-K
rc<-1/(K*(1-exp(-s*K)))

rlist<-sort(c(0.002,0.004,0.006,0.008,0.01,0.015,rc,0.022,0.026))

@@

# plot for local dispersal in D matrix 
pdf(paste(resloc,"abrewer_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.2))
for(i in c(1:length(rlist))){
    r<-rlist[i]
    params<-c(r,K,s)
    ext_thrs<-p0/10
    s0<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,ploton = F)
    abrewer_extrisk_d0$risk_left_d0[i]<-s0$risk_left[1]
    abrewer_extrisk_d0$risk_right_d0[i]<-s0$risk_right[1]
    plot(s0$d_seq,s0$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),
         xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s0$d_seq,s0$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

saveRDS(abrewer_extrisk_d0,paste(resloc,"abrewer_extrisk_d0.RDS",sep=""))

# plot for global dispersal in D matrix 
pdf(paste(resloc,"abrewer_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.2))
for(r in rlist){
    params<-c(r,K,s)
    ext_thrs<-p0/10
    s0<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,ploton = F)
    plot(s0$d_seq,s0$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),
         xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s0$d_seq,s0$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# Plot ext_risk_d0
abrewer_extrisk_d0$CI0.025left<-qbinom(p=0.025,size=numsims,prob=abrewer_extrisk_d0$risk_left_d0)/numsims
abrewer_extrisk_d0$CI0.975left<-qbinom(p=0.975,size=numsims,prob=abrewer_extrisk_d0$risk_left_d0)/numsims

abrewer_extrisk_d0$CI0.025right<-qbinom(p=0.025,size=numsims,prob=abrewer_extrisk_d0$risk_right_d0)/numsims
abrewer_extrisk_d0$CI0.975right<-qbinom(p=0.975,size=numsims,prob=abrewer_extrisk_d0$risk_right_d0)/numsims

pdf(paste(resloc,"abrewer_extrisk_d0.pdf",sep=""),height=6,width=6)
plot(abrewer_extrisk_d0$r,abrewer_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(abrewer_extrisk_d0$r),xlab="r",ylab="ext_risk",cex.lab=1.5,pch=1)
arrows(x0=abrewer_extrisk_d0$r,y0=abrewer_extrisk_d0$CI0.025left,x1=abrewer_extrisk_d0$r,
       y1=abrewer_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)

@@

```{r fig_verhulst_scl_2.5, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)

@@

rlist<-seq(from=0.2,to=1.8,by=0.2)

@@

# plot for local dispersal in D matrix 
pdf(paste(resloc,"verhulst_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.2))
for(i in c(1:length(rlist))){
    r<-rlist[i]
    ext_thrs<-p0/10
    s0<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=r,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,ploton = F)
    verhulst_extrisk_d0$risk_left_d0[i]<-s0$risk_left[1]
    verhulst_extrisk_d0$risk_right_d0[i]<-s0$risk_right[1]
    plot(s0$d_seq,s0$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),
         xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s0$d_seq,s0$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

saveRDS(verhulst_extrisk_d0,paste(resloc,"verhulst_extrisk_d0.RDS",sep=""))

# plot for global dispersal in D matrix 
pdf(paste(resloc,"verhulst_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.2))
for(r in rlist){
    ext_thrs<-p0/10
    s0<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=r,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,ploton = F)
    plot(s0$d_seq,s0$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),
         xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s0$d_seq,s0$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# Plot ext_risk_d0
verhulst_extrisk_d0$CI0.025left<-qbinom(p=0.025,size=numsims,prob=verhulst_extrisk_d0$risk_left_d0)/numsims
verhulst_extrisk_d0$CI0.975left<-qbinom(p=0.975,size=numsims,prob=verhulst_extrisk_d0$risk_left_d0)/numsims

@@

pdf(paste(resloc,"verhulst_extrisk_d0.pdf",sep=""),height=6,width=6)
plot(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(verhulst_extrisk_d0$r),xlab="r",ylab="ext_risk",cex.lab=1.5,pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025left,x1=verhulst_extrisk_d0$r,
       y1=verhulst_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)

>>>>

pdf("./Results/hassell/hassell_extrisk_d0.pdf",height = 6,width=6)
plot(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = c(1.4,7.6),
     xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025left,
       x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_hassell,lty="dotted")

@@

pdf(paste(resloc,"msmith_extrisk_d0.pdf",sep=""),height=6,width=6)
plot(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = c(1.2,2.8),
     xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025left,
       x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_msmith,lty="dotted")

@@

```{r sim_pennycuick, echo=F,  results="hide", cache=T, cache.extra=list(seed,a_pennycuick,b_pennycuick,rc_pennycuick,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

model<-"pennycuick"

@@

#for local dispersal in D matrix 
res_pennycuick_local<-c()

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,a,b)
    K_e<-(b/a)*(a+log(r-1))
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right)
    res_pennycuick_local<-abind(res_pennycuick_local,temp_mat,along = 3)

    pennycuick_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    pennycuick_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
}

anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_pennycuick_local)<-list(NULL,cnm,anm)

saveRDS(pennycuick_extrisk_d0,paste(resloc,"pennycuick_extrisk_d0.RDS",sep=""))
saveRDS(res_pennycuick_local,paste(resloc,"res_pennycuick_local.RDS",sep=""))

# For global dispersal in D matrix 
res_pennycuick_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,a,b)
    K_e<-(b/a)*(a+log(r-1))
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right)
    res_pennycuick_global<-abind(res_pennycuick_global,temp_mat,along = 3)
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_pennycuick_global)<-list(NULL,cnm,anm)
saveRDS(res_pennycuick_global,paste(resloc,"res_pennycuick_global.RDS",sep=""))
```

```{r fig_pennycuick, echo=F, results="hide",cache=T, cache.extra=list(seed,res_pennycuick_local,res_pennycuick_global)}
pdf(paste(resloc,"pennycuick_ext_risk_local_disp.pdf",sep=""),height=9,width=15)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,6.2))

for(i in 1:dim(res_pennycuick_local)[3]){
  s<-res_pennycuick_local[,,i]
  s<-as.data.frame(s)

pdf(paste(resloc,"pennycuick_ext_risk_global_disp.pdf",sep=""),height=9,width=15)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,6.2))

for(i in 1:dim(res_pennycuick_global)[3]){
  s<-res_pennycuick_global[,,i]
  s<-as.data.frame(s)

@@

pdf("./Results/pennycuick/pennycuick_extrisk_d0.pdf",height = 6,width=6)
plot(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = c(2,7),xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025left,
       x1=pennycuick_extrisk_d0$r,y1=pennycuick_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_pennycuick,lty="dotted")

@@

```{r sim_abrewer, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

numsims<-10000
numsteps<-25
numlocs<-5
s<-0.2
K<-50
p0<-K
rc_abrewer<-1/(K*(1-exp(-s*K)))

rlist<-sort(c(0.002,0.004,0.006,0.008,0.01,0.015,rc_abrewer,0.022,0.026))

@@

#for local dispersal in D matrix 
res_abrewer_local<-c()

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,K,s)
    ext_thrs<-p0/10

    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right)
    res_abrewer_local<-abind(res_abrewer_local,temp_mat,along = 3)

    abrewer_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    abrewer_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
}

anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_abrewer_local)<-list(NULL,cnm,anm)

saveRDS(abrewer_extrisk_d0,paste(resloc,"abrewer_extrisk_d0.RDS",sep=""))
saveRDS(res_abrewer_local,paste(resloc,"res_abrewer_local.RDS",sep=""))

# For global dispersal in D matrix 
res_abrewer_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,K,s)
    ext_thrs<-p0/10

    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right)
    res_abrewer_global<-abind(res_abrewer_global,temp_mat,along = 3)
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_abrewer_global)<-list(NULL,cnm,anm)
saveRDS(res_abrewer_global,paste(resloc,"res_abrewer_global.RDS",sep=""))
```

```{r fig_abrewer, echo=F, results="hide",cache=T, cache.extra=list(seed,res_abrewer_local,res_abrewer_global)}
pdf(paste(resloc,"abrewer_ext_risk_local_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))

for(i in 1:dim(res_abrewer_local)[3]){
  s<-res_abrewer_local[,,i]
  s<-as.data.frame(s)

pdf(paste(resloc,"abrewer_ext_risk_global_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))

for(i in 1:dim(res_abrewer_global)[3]){
  s<-res_abrewer_global[,,i]
  s<-as.data.frame(s)

```{r fig_abrewer_extrisk_d0, echo=F,results="hide"}
set.seed(seed)
numsims<-10000
abrewer_extrisk_d0<-readRDS(paste(resloc,"abrewer_extrisk_d0.RDS",sep=""))

abrewer_extrisk_d0$CI0.025left<-qbinom(p=0.025,size=numsims,prob=abrewer_extrisk_d0$risk_left_d0)/numsims
abrewer_extrisk_d0$CI0.975left<-qbinom(p=0.975,size=numsims,prob=abrewer_extrisk_d0$risk_left_d0)/numsims
abrewer_extrisk_d0$CI0.025right<-qbinom(p=0.025,size=numsims,prob=abrewer_extrisk_d0$risk_right_d0)/numsims
abrewer_extrisk_d0$CI0.975right<-qbinom(p=0.975,size=numsims,prob=abrewer_extrisk_d0$risk_right_d0)/numsims
pdf(paste(resloc,"abrewer_extrisk_d0.pdf",sep=""),height=6,width=6)
plot(abrewer_extrisk_d0$r,abrewer_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(abrewer_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=abrewer_extrisk_d0$r,y0=abrewer_extrisk_d0$CI0.025left,x1=abrewer_extrisk_d0$r,
       y1=abrewer_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_abrewer,lty="dotted")

@@

```{r sim_verhulst, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

rlist<-seq(from=0.2,to=1.8,by=0.2) #rc=1

@@

#for local dispersal in D matrix 
res_verhulst_local<-c()

for(i in c(1:length(rlist))){
    r<-rlist[i]
    params<-r
    ext_thrs<-p0/10

    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right)
    res_verhulst_local<-abind(res_verhulst_local,temp_mat,along = 3)

    verhulst_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    verhulst_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
}

anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_verhulst_local)<-list(NULL,cnm,anm)

saveRDS(verhulst_extrisk_d0,paste(resloc,"verhulst_extrisk_d0.RDS",sep=""))
saveRDS(res_verhulst_local,paste(resloc,"res_verhulst_local.RDS",sep=""))

# For global dispersal in D matrix 
res_verhulst_global<-c()
for(r in rlist){
    params<-r
    ext_thrs<-p0/10

    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right)
    res_verhulst_global<-abind(res_verhulst_global,temp_mat,along = 3)
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_verhulst_global)<-list(NULL,cnm,anm)
saveRDS(res_verhulst_global,paste(resloc,"res_verhulst_global.RDS",sep=""))
```

```{r fig_verhulst, echo=F, results="hide",cache=T, cache.extra=list(seed,res_verhulst_local,res_verhulst_global)}
pdf(paste(resloc,"verhulst_ext_risk_local_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))

for(i in 1:dim(res_verhulst_local)[3]){
  s<-res_verhulst_local[,,i]
  s<-as.data.frame(s)

pdf(paste(resloc,"verhulst_ext_risk_global_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))

for(i in 1:dim(res_verhulst_global)[3]){
  s<-res_verhulst_global[,,i]
  s<-as.data.frame(s)

```{r fig_verhulst_extrisk_d0, echo=F,results="hide"}
set.seed(seed)
numsims<-10000
verhulst_extrisk_d0<-readRDS(paste(resloc,"verhulst_extrisk_d0.RDS",sep=""))

verhulst_extrisk_d0$CI0.025left<-qbinom(p=0.025,size=numsims,prob=verhulst_extrisk_d0$risk_left_d0)/numsims
verhulst_extrisk_d0$CI0.975left<-qbinom(p=0.975,size=numsims,prob=verhulst_extrisk_d0$risk_left_d0)/numsims

@@

pdf(paste(resloc,"verhulst_extrisk_d0.pdf",sep=""),height=6,width=6)
plot(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(verhulst_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025left,x1=verhulst_extrisk_d0$r,
       y1=verhulst_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=1,lty="dotted")
